Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-17 TACAS2018/paper.tex
edits sec 6

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Error modelling and soundness}\label{sec:errors}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%-------------------------------
\section{Specification of control systems properties} 
\label{sec:specification}
%-------------------------------
\todo{all this section needs to be merged with the next one and only
discussed for an observed model.}

%-------------------------------
\subsection{Stability} 
\label{ssec:stabspecification}
%-------------------------------

In this work we are interested in asymptotic stability: asymptotic
stability is a property that amounts to convergence of the model
executions to an equilibrium point, starting from any states in a
neighborhood of the point.

@@

%-------------------------------
\subsection{Safety} 
\label{ssec:safespecification}
%-------------------------------

@@

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%% In most real implementations, the internal state of a plant cannot be
%% directly measured but rather inferred from its
%% effect on the output. A plant model that minimises the difference
%% between the outputs is called an observer and it is a well known
%% paradigm in the control literature~\cite{astrom1997computer}.

Since we are interested in synthesising controllers with observer
designs, in this section we will look at checking stability and safety
in the presence of an observer.

%the challenges presented by the introduction of the observer.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization. We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations. For simplicity of the description, we will agregate the noises as follows:
\begin{align*}
\eta_1&=\nu_1+\nu_1'+\nu_t\\
\eta_2&=\nu_2+\nu_2'
\end{align*}
where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
A controllable and observable system will have the following dynamics:
\begin{align}
\scriptstyle
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer, and $k_r$ is a reference gain required by the model.

As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion on these polynomials
to assert the stability specification.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System with FWL effects}\label{sec:cof_fwl_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{FWL effects here? they are implicit from equation \ref{eq:observer_LTI_FWL_cf}}

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Error modelling}\label{sec:errors}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%% %-------------------------------
%% \section{Specification of control systems properties} 
%% \label{sec:specification}
%% %-------------------------------

%% %-------------------------------
%% \subsection{Stability} 
%% \label{ssec:stabspecification}
%% %-------------------------------

%% %-------------------------------
%% \subsection{Safety} 
%% \label{ssec:safespecification}
%% %-------------------------------

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Properties of a controllable observed system}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%% In most real implementations, the internal state of a plant cannot be
%% directly measured but rather inferred from its
%% effect on the output. A plant model that minimises the difference
%% between the outputs is called an observer and it is a well known
%% paradigm in the control literature~\cite{astrom1997computer}.

Since we are interested in synthesising controllers with observer
designs, in this section we will look at checking stability, safety
and the response time in the presence of an observer.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an observed system}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In this work we are interested in asymptotic stability: asymptotic
stability is a property that amounts to convergence of the model
executions to an equilibrium point, starting from any states in a
neighborhood of the point.

@@

Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization. We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations. For simplicity of the description, we will agregate the noises as follows:
\begin{align*}
\eta_1&=\nu_1+\nu_1'+\nu_t\\
\eta_2&=\nu_2+\nu_2'
\end{align*}
where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
A controllable and observable system will have the following dynamics:
\begin{align}
\scriptstyle
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer, and $k_r$ is a reference gain required by the model.

As stated in Section~\ref{sec:cof_stability}, we use Jury's Criterion on these polynomials
to assert the stability specification.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an observed system with FWL effects}\label{sec:cof_fwl_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a digitally observed system}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{FWL effects here? they are implicit from equation \ref{eq:observer_LTI_FWL_cf}}

@@

%==========

@@
